### 2017-05-29 sheets/basis-3/sheet-basis-3.tex
WIP: Solution for 3.2

@@

\begin{answer}
  \begin{itemize}
    \item[(a)]
      $\Sym(f) = \lambda g.f \circ g$, where $g$ is a permutation\\
      $\Ord(f) = \lambda (a, b).(f(a), f(b))$, where $a, b \in X$
    \item[(b)]
      Let's consider a non-identity permutation $h$. We can build an ordering
      from it by taking $(x, h(x))$ as an element of ordering relation for
      $\forall x \in \text{ some finite set } X$, then filling the gaps by
      reflexivity and transitivity.

      However, it's not the case for an identity permutation $i$, as for that
      permutation the $i(x) = x$ which leaves us only with reflexivity pairs if
      we try to build an ordering from that bijection. Thus, we cannot define
      formation of an ordering from an identity permutation and therefore
      there's no natural transformation from $\Sym$ to $\Ord$.
    \item[(c)]
      $|\Sym(X)| = n$!\\
      $|\Ord(X)| = n$!
  \end{itemize}
  We have seen that there's no natural transformation $\Sym \to \Ord$.
  Nonetheless, we have also seen that they have the same number of
  elements and an isomorphism between them can actually be formed: it's not
  hard to construct all permutations or orderings of some finite set knowing
  its elements.

  This leads us to the conclusion that $\Sym(X) \iso \Ord(X)$ for all $X \in
  \cat{B}$, but not \emph{naturally} in $X \in \cat{B}$.
\end{answer}

@@

@@

                    %TODO

@@

>>>>

\begin{answer}
  We have to give two functors
  $H \from \ftrcat{\cat{A}^\op}{\cat{B}^\op} \to \ftrcat{\cat{A}}{\cat{B}}^\op$
  and
  $J \from \ftrcat{\cat{A}}{\cat{B}}^\op \to \ftrcat{\cat{A}^\op}{\cat{B}^\op}$
  such that $H \circ J = 1_{\ftrcat{\cat{A}}{\cat{B}}^\op}$ and $J \circ H = 1_{\ftrcat{\cat{A}^\op}{\cat{B}^\op}}$.

  First we define $H$. For that we first map objects of
  $\ftrcat{\cat{A}^\op}{\cat{B}^\op}$ (being itself functors from $\cat{A}^\op$ to $\cat{B}^\op$)
  to objects of $\ftrcat{\cat{A}}{\cat{B}}^\op$ (being itself functors from $\cat{A}$ to $\cat{B}$).

  Let $F\from \cat{A}^\op \to \cat{B}^\op$ be an object of $\ftrcat{\cat{A}^\op}{\cat{B}^\op}$.
  Because every object $A : \cat{A}^\op$ is also an object of $\cat{A}$ we can define
  $H(F)(A) := F(A)$.
  Now let $f \from A \to B$ be an morphism in $\cat{A}^\op$. We have $F(f^\op)=g^\op$ for some morphism $g$ in $\cat{B}^\op$.
  We define $H(F)(f) := F(f^\op)^\op = g$.

  Now let $F, G \from \cat{A}^\op \to \cat{B}^\op$ be objects and
  $\alpha \from F \to G$ be an morphism of $\ftrcat{\cat{A}^\op}{\cat{B}^\op}$.
  $\alpha = (F(A) \stackrel{\alpha_A}{\to} G(A))_A$ is an natural transformation.
  We define $H(\alpha) := \beta \from H(G) \to H(F) := (\alpha_A^\op)_A$ and have to show that $\beta$ is indeed such a natural transformation.
  Let $A, A' : \cat{A}$ and $f \from A \to A'$. We have to show that the following diagram commutes:
  \[
    \begin{tikzcd}
      H(G)(A) \arrow{r}{H(G)(f)} \arrow{d}{H(\alpha)_A} & H(G)(A') \arrow{d}{H(\alpha)_A'} \\
      H(F)(A) \arrow{r}{H(F)(f)} & H(F)(A')
    \end{tikzcd}
  \]
  By unfolding the definition of $H$ this diagram commutes if and only if the following diagram commutes:
  \[
    \begin{tikzcd}
      G(A) & G(A') \arrow{l}{G(f^\op)} \\
      F(A) \arrow{u}{\alpha_A} & F(A') \arrow{l}{F(f^\op)} \arrow{u}{\alpha_{A'}}
    \end{tikzcd}
  \]
  This diagram commutes because $\alpha$ is a natural transformation.

  Secondly we define $J$ using a similar construction as above and get
  $H \circ J = 1_{\ftrcat{\cat{A}}{\cat{B}}^\op}$ and $J \circ H = 1_{\ftrcat{\cat{A}^\op}{\cat{B}^\op}}$.

  Now by definition of $\iso$,
  $\ftrcat{\cat{A}^\op}{\cat{B}^\op} \iso \ftrcat{\cat{A}}{\cat{B}}^\op$
  holds.
\end{answer}

@@

\begin{answer}
  In the following we will consider a representation of the permutation as a
  tuple of two elements $(a, b)$, where $a \mapsto b$ is an element of a
  bijection.
  \begin{itemize}
    \item[(a)]
      For any $A \in ob(\cat{B}), C \in ob(\Set), f: A \to C$
      \begin{align*}
        \Sym(f) &= \lambda (a, b). (f(a), f(b))\\
        \Ord(f) &= \lambda (a, b).(f(a), f(b))
      \end{align*}
    \item[(b)]
      Let's fix a finite set $A$ and define $\Sym \to \Ord$ on it.\\
      \begin{align*}
        A &= \{a, b\}\\
        \Sym(A) &= \{\{(a, a), (b, b)\}, \{(a, b), (b, a)\}\}\\
        \Ord(A) &= \{\{(a, b), (a, a), (b, b)\}, \{(b, a), (a, a), (b, b)\}\},\\
      \end{align*}
      Natural transformation $\alpha: \Sym(A) \to \Ord(A)$:\\
      \begin{align*}
        \alpha_A(\{(a, a), (b, b)\}) &= \{(a, b), (a, a), (b, b)\}\\
        \alpha_A(\{(a, b), (b, a)\}) &= \{(b, a), (a, a), (b, b)\}
      \end{align*}
      And a permutation of $A$:
      \begin{align*}
        f(a) &= b\\
        f(b) &= a
      \end{align*}
      Now, for $\alpha$ to indeed be a natural transformation, the  naturality
      axiom should hold for all arrows $A \to A$, including $f$. Let's check if
      it holds by applying $f$.\\
      \begin{align*}
        &\alpha_A(f(\{(a, a), (b, b)\})) &= \alpha_A(\{(b, b), (a, a)\}) =&& \{(b, a), (b, b), (a, a)\}\\
        &\alpha_A(f(\{(a, b), (b, a)\})) &= \alpha_A(\{(b, a), (a, b)\}) =&& \{(a, b), (b, b), (a, a)\}
      \end{align*}
      Here $\alpha_A$ contradicts our definition of it and we can conclude that
      it is not a natural transformation. The only other possibility of
      defining $\alpha_A$ would be to switch the images of sets in the
      definition, but the applying $f$ will yield us a similar contradictory
      result.  From this we see that no matter how we define $\alpha_A$, the
      naturality axiom will not hold for our $f$, hence we cannot have a
      natural transformation for $\Sym(A) \to \Ord(A)$ and, in general, a
      natural transformation $\Sym \to \Ord$.
    \item[(c)]
      From combinatorics we know that the number of all permutations of a
      finite set of size $n$ is exactly $n$!:\\
      \begin{equation*}
        |\Sym(X)| = n!
      \end{equation*}
      We can also notice that we may consider permutations as an order too,
      hence the number of all orders is:
      \begin{equation*}
        |\Ord(X)| = n!
      \end{equation*}
  \end{itemize}
  So we know that $\Sym$ and $\Ord$ have exactly the same number of elements
  and generally we can come up with a mapping between those elements, such that
  $\Sym(X) \iso \Ord(X)$ for all $X \in \cat{B}$. However, we have also shown
  that we cannot define a natural transformation $\Sym \to \Ord$ which gives
  that there's no natural isomorphism between those categories.
\end{answer}

@@

                    By analogous reasoning using $\epsln$ we obtain that $G$ is also faithful.

@@

@@

                    We define $f := \eta_{A'}^{-1} \circ G(g) \circ \eta_A$ and use the naturality axiom for $\eta$ in order to get:
                        G(F(f)) & = \eta_A' \circ f \circ \eta_A^{-1}\\
                                & = \eta_A' \circ \eta_{A'}^{-1} \circ G(g) \circ \eta_A \circ \eta_A^{-1}\\
                                & = G(g)
                    Since $G$ is faithful we obtain $F(f) = g$.
                    Thus $F$ is full.
